Adaptive broadcast tree for multicores

### 2013-06-04 graphs/visu_gruyere_mst.tex
Added forgotten file

\node at (0mm,480mm) {Machine: gruyere, topology: cluster};
\node[draw,fill=red!20,minimum size=10mm] (s_0_8) at (50mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (60mm,0mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (80mm,60mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_4_12) at (90mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_16) at (100mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (110mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (120mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (130mm,60mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_8) at (80mm,120mm) {};
\draw[->,very thick,color=red] (s_0_8.center) -- (r_0_8.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_8_20) at (90mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_24) at (100mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (110mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (120mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (130mm,120mm) {};

@@

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_8_24) at (120mm,360mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (130mm,360mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (140mm,360mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_24_25) at (150mm,360mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_12) at (120mm,180mm) {};
\draw[->,very thick,color=red] (s_4_12.center) -- (r_4_12.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_12_28) at (130mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (140mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (150mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (160mm,180mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_20) at (120mm,300mm) {};
\draw[->,very thick,color=red] (s_8_20.center) -- (r_8_20.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (130mm,300mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (140mm,300mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (150mm,300mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (121mm,165mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (121mm,105mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_16) at (130mm,240mm) {};
\draw[->,very thick,color=red] (s_4_16.center) -- (r_4_16.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (140mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (150mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (160mm,240mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (131mm,150mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (131mm,90mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (141mm,75mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_24_27) at (141mm,405mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (141mm,135mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (141mm,345mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_12_28) at (150mm,420mm) {};
\draw[->,very thick,color=red] (s_12_28.center) -- (r_12_28.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (160mm,420mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (170mm,420mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (180mm,420mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (151mm,330mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (151mm,225mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (151mm,285mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (151mm,390mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (161mm,315mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (161mm,270mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_24_25) at (161mm,375mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (161mm,210mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (171mm,255mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (171mm,465mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (171mm,195mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (181mm,450mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (191mm,435mm) {};

>>>>

\node at (0mm,480mm) {Machine: gruyere, topology: mst};
\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (50mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_16) at (60mm,0mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (70mm,60mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_4_8) at (80mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_20) at (90mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (100mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (110mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (120mm,60mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_16) at (80mm,240mm) {};
\draw[->,very thick,color=red] (s_0_16.center) -- (r_0_16.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (90mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (100mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (110mm,240mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_4_8) at (100mm,120mm) {};
\draw[->,very thick,color=red] (s_4_8.center) -- (r_4_8.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_8_28) at (110mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_24) at (120mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_12) at (130mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (140mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (150mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (160mm,120mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (101mm,285mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_20) at (110mm,300mm) {};
\draw[->,very thick,color=red] (s_4_20.center) -- (r_4_20.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (120mm,300mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (130mm,300mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (140mm,300mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (111mm,105mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (111mm,270mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (121mm,255mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (121mm,90mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_28) at (130mm,420mm) {};
\draw[->,very thick,color=red] (s_8_28.center) -- (r_8_28.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (140mm,420mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (150mm,420mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (160mm,420mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (131mm,345mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (131mm,75mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_24) at (140mm,360mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (150mm,360mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (160mm,360mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_24_25) at (170mm,360mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (141mm,330mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_12) at (150mm,180mm) {};
\draw[->,very thick,color=red] (s_8_12.center) -- (r_8_12.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (160mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (170mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (180mm,180mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (151mm,165mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (151mm,465mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (151mm,315mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (161mm,450mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_24_27) at (161mm,405mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (161mm,150mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (171mm,225mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (171mm,390mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (171mm,435mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (171mm,135mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (181mm,210mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_24_25) at (181mm,375mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (191mm,195mm) {};

@@

### 2013-06-04 graphs/visu_gruyere_ring.tex
Added forgotten file

\node at (0mm,480mm) {Machine: gruyere, topology: mst};
\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (50mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_16) at (60mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (70mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (80mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (90mm,0mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (70mm,60mm) {};
\draw[->,very thick,color=red] (s_0_4.center) -- (r_0_4.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_4_8) at (80mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_20) at (90mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (100mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (110mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (120mm,60mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_16) at (80mm,240mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (90mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (100mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (110mm,240mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (81mm,45mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (91mm,30mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_4_8) at (100mm,120mm) {};
\draw[->,very thick,color=red] (s_4_8.center) -- (r_4_8.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_8_28) at (110mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_24) at (120mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_12) at (130mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (140mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (150mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (160mm,120mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (101mm,15mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (101mm,285mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_4_20) at (110mm,300mm) {};
\draw[->,very thick,color=red] (s_4_20.center) -- (r_4_20.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (120mm,300mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (130mm,300mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (140mm,300mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (111mm,105mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (111mm,270mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (121mm,255mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (121mm,90mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_28) at (130mm,420mm) {};
\draw[->,very thick,color=red] (s_8_28.center) -- (r_8_28.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (140mm,420mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (150mm,420mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (160mm,420mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (131mm,345mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (131mm,75mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_24) at (140mm,360mm) {};
\draw[->,very thick,color=red] (s_8_24.center) -- (r_8_24.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (150mm,360mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (160mm,360mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_24_25) at (170mm,360mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (141mm,330mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_8_12) at (150mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (160mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (170mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (180mm,180mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (151mm,165mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (151mm,465mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (151mm,315mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (161mm,450mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_24_27) at (161mm,405mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (161mm,150mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (171mm,225mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (171mm,390mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (171mm,435mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (171mm,135mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (181mm,210mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_24_25) at (181mm,375mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (191mm,195mm) {};

>>>>

\node at (0mm,480mm) {Machine: gruyere, topology: ring};
\node[draw,fill=red!20,minimum size=10mm] (s_8_4) at (50mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_12) at (60mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (70mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (80mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (90mm,120mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_4) at (70mm,60mm) {};
\draw[->,very thick,color=red] (s_8_4.center) -- (r_8_4.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_4_0) at (80mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (90mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (100mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (110mm,60mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_12) at (80mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_28) at (90mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (100mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (110mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (120mm,180mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (81mm,165mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (91mm,150mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_0) at (100mm,0mm) {};
\draw[->,very thick,color=red] (s_4_0.center) -- (r_4_0.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_0_16) at (110mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (120mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (130mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (140mm,0mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (101mm,105mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (101mm,135mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_12_28) at (110mm,420mm) {};
\draw[->,very thick,color=red] (s_12_28.center) -- (r_12_28.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_28_24) at (120mm,420mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (130mm,420mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (140mm,420mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (150mm,420mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (111mm,225mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (111mm,90mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (121mm,75mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (121mm,210mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_16) at (130mm,240mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_16_20) at (140mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (150mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (160mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (170mm,240mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (131mm,195mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (131mm,45mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_28_24) at (140mm,360mm) {};
\draw[->,very thick,color=red] (s_28_24.center) -- (r_28_24.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_24_8) at (150mm,360mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (160mm,360mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (170mm,360mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_24_25) at (180mm,360mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (141mm,30mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (141mm,465mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (151mm,450mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (151mm,15mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_16_20) at (160mm,300mm) {};
\draw[->,very thick,color=red] (s_16_20.center) -- (r_16_20.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_20_8) at (170mm,300mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (180mm,300mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (190mm,300mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (200mm,300mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (161mm,435mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (161mm,285mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_24_8) at (170mm,120mm) {};
\draw[->,very thick,color=red] (s_24_8.center) -- (r_24_8.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_24_27) at (171mm,405mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (171mm,270mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (181mm,255mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (181mm,390mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_24_25) at (191mm,375mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (191mm,345mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_20_8) at (200mm,120mm) {};
\draw[->,very thick,color=red] (s_20_8.center) -- (r_20_8.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (201mm,330mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (211mm,315mm) {};

@@
